\hfill \break

Foremost, I would like to express my sincere gratitude to my advisor Dr. Naeemul Hassan for the continued support and knowledge while guiding me throughout my thesis. I cannot overstate my gratitude for the degree of patience and understanding demonstrated with me throughout this process and the contribution Dr. Hassan brings to the computer science department.

In addition to my advisor, I would also like to thank my other readers: Dr. Kirsten Dellinger and Dr. Dawn Wilkins for their insight, questions, and flexibility.

My sincerest thanks also goes to the computer science department at the University of Mississippi, for accepting an art student with no background in computer science and developing me into the competent programmer I am now. Thank you to the Sally McDonnell Barksdale Honors College faculty and staff for the opportunities and challenges given to me these past five years.

Thank you to everyone who participated in this project and took the time to read my research on sexual harassment, my categorization rules, and assist me in manually categorizing a set of tweets: John Joseph Angel, Ainsley Ash, Tim Dolan, Jason Hale, Lily Hassan, Gracie Hubacek, Karen Hubacek, Krish Lamba, Will Lewis, Mallory Loe, Ethan Luckett, Jake Wooley, Lina Ye, Dr. John Wiginton, and Dr. Debra Young.

I would also like to thank the Title IX office and Department of Violence Prevention for the accommodations, help, and support given during my own struggles throughout this past year. Thank you for empowering me with the knowledge and support I needed to finish my last undergraduate year, and for inspiring me to take this direction with my thesis.

Lastly, I would like to thank my family and friends who have supported me throughout this thesis as well as my undergraduate career. Looking back on my transcript and resume as I prepare to graduate, I see nothing but the contributions of my support system and how my achievements would not have been possible alone. Without your patience and support, I would not have finished. In particular I would like to thank Dr. Kristin Davidson, Gracie Hubacek and Ethan Luckett for not only your help in all my academic challenges but also for your unending support as friends. I would like to extend a special thank you to my pet rabbits who have continued to inspire and motivate me every day since I have loved them: Ellie, Ezra, and Buddy.
